### 2017-12-05 proposal/proposal.tex
Stash

In the last decade, astrophysical systems with one white dwarf orbiting another
body e.g.\ a black hole or another white dwarf (referred to collectively as WD
binaries) have become increasingly important for several topics in astrophysics.
As gravitational wave (GW) astronomy takes off with the recent triumphs of the
Laser Interferometer Gravitational-Wave Observatory (LIGO), understanding GW
profiles of WD systems is paramount. Mergers of WD-WD binaries create a variety
of astrophysical systems, the most important of which are type Ia supernovae,
the standard candle of observational astronomy. WD-BH (black hole) systems are
expected to produce detectable flares that can be observed to yield constraints
on currently unknown physics.
% (https://arxiv.org/pdf/1701.08162.pdf)

>>>>

In the last decade, astrophysical systems with one white dwarf and another
body (e.g.\ a black hole or another white dwarf), referred to collectively as WD
binaries, have become increasingly important for several topics in astrophysics.
Mergers of WD-WD binaries create a variety of astrophysical systems, the most
important of which are type Ia supernovae, the standard candle of observational
astronomy. WD-BH (black hole) systems are expected to produce detectable flares
that can be observed to yield constraints on currently unknown physics
(https://arxiv.org/pdf/1701.08162.pdf).
